Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
remove unnecessary comment
changing title, no acronym
abstract+results update+sec4.1

\title{Demystifying the Dynamic Slicing and SFL Combination}

@@

\begin{abstract}
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
techniques and normally seen as complementary.  This paper reports the outcome
of a study using real-world applications with the goal of demystifying the
impact of combining \ds{} with \sfl{}.  We suspect that several highly
suspicious components---often involved in failing, but seldom in passing
executions---may be unrelated to the bug. With the aforementioned combination,
such components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key limitation---the risk
of missing faulty statements. Our results show that, in practice, \ds{} rarely
misses faulty statements (22 misses in 256 cases) and that the
\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
in \Rui{x\% on average}. To sum, we found that, despite tacit opinions of the
research community about the usefulness of \ds{} in automated debugging, we
found the combination practical and effective, and encourage new \sfl{}
techniques to be evaluated against that optimization.
\end{abstract}

@@

To evaluate our approach, we compare the cost of diagnosing
a collection of faulty versions using \sfl{} versus \comb{}.

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (LOC)$^{*}$ & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            &   & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           &   & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         &   & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           &   & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           &   & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         &   & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}

@@

\Sof{@todo: Add pie chart to show the distribution of foos}

@@

        \lang{}            & 1.42\% & 30.47\%\\
        \cmath{}           & 9.88\% & 11.43\%\\
        %\closure{}          &  & \\
		\chart{}			& 59.30\% & 53.64\% \\
        \jtime{}            & 17.27\% & 32.02\%\\
        \mockito{}          & 16.54\% & 21.67\%\\

@@

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  54 & 84.4\%  & 54  & 84.4\%
		 				& 64 & 100\% & 62 & 96.9\% & 64      \\
		\cmath{}           & 82 & 81.2\%  & 86 & 85.1\%
						& 90 & 89.1\% & 97 & 96.0\% & 101  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 203  &  & 213 &
	 				& 223 &  & 234 &  & 256 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

@@

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 522.47     & 684.89   & 611.04   \\ \midrule
Median & 50.375      & 66.25               & 54.3                \\ \midrule
Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{@tofix: Need to center ylabels}}
		\label{fig:performance}
\end{figure}

>>>>

\title{Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault
Localization}

@@

\begin{abstract}
Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis.  Dynamic Slicing (\ds{}) and
Spectrum-based Fault Localization (\sfl{}) are very popular fault diagnosis
techniques and normally seen as complementary.  This paper reports the outcome
of a study using real-world applications with the goal of demystifying the
impact of combining \ds{} with \sfl{}.  We suspect that several highly
suspicious components---often involved in failing, but seldom in passing
executions---may be unrelated to the bug. With the aforementioned combination,
such components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key limitation---the risk
of missing faulty statements. Our results show that, in practice, \ds{} rarely
misses faulty statements (23 misses in 260 cases) and that the
\ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic accuracy
in 51\% of the faults. To sum, we found that, despite tacit opinions of the
research community about the usefulness of \ds{} in automated debugging, we
found the combination practical and effective, and encourage new \sfl{}
techniques to be evaluated against that optimization.
\end{abstract}

@@

To evaluate our approach, we compare the cost of diagnosing
a collection of faults using \sfl{} versus \comb{}.

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
     Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}

@@

\begin{figure}[h]
	\vspace{-1.5cm}

		\centering
		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
		\vspace{-1cm}

		\caption{FAULT$\_$OF$\_$OMISSION distribution in the \dfj{} dataset}
		\label{fig:foos}
\end{figure}

Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of the faults of this dataset are FOOs.

@@

        \lang{}            & 1.40\% & 31.46\%\\
        \cmath{}           & 10.30\% & 12.34\%\\
        %\closure{}          &  & \\
		\chart{}			& 59.30\% & 53.64\% \\
        \jtime{}            & 17.27\% & 32.02\%\\
        \mockito{}          & 16.54\% & 21.67\%\\

@@

		            & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$
					& \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}         &  55 & 84.6\%  & 55  & 84.6\%
		 				& 65 & 100\% & 63 & 96.9\% & 65      \\
		\cmath{}           & 85 & 81.7\%  & 89 & 85.6\%
						& 93 & 89.4\% & 99 & 95.2\% & 104  \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}          & 22 & 84.6\% & 24 & 92.3\%
						& 20 & 76.9\% & 22 & 84.6\% & 26    \\
		\jtime{}          & 21 & 77.8 \% & 22 & 81.5 \%
				& 22 & 81.5\% & 23 & 85.2\% & 27     \\
		 \mockito{}      & 24  & 63.2\% & 27 & 71.1\%
		 				& 27 & 71.1\% & 30 & 78.9\% & 38 \\\midrule
	 Total      & 207  & 78.4\% & 217 & 83.0\%
	 				& 227 & 83.8\% & 237 & 88.2\% & 260 \\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL-5      & SFL-10              & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule
Median & 49.38    & 53.00  & 69.25              & 56.93               \\ \midrule
Variance & 1223.08  &  1148.11  & 1352.37  & 1294.87   \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

\begin{figure}[h]
	\vspace{-1.5cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results}
		\label{fig:performance}
\end{figure}
